Software Citation Principles

### 2016-07-21 sc-principles/rebuttal/rebuttal.tex

While I think this is a very useful paper, I see the following problems with the current version:
}

\begin{enumerate}
\item \textbf{Reviewer comment:}
\emph{The logical connections between the different parts of the paper are not clear. For example, how do the ``basic requirements'' of Table 2 map to the ``principles'' in Section 1? And are the principles presented in the beginning the *outcome* of this research (this is what lines 29+ seem to suggest) or are they *assumptions* of the approach to be discussed and evaluated (this is how they seem to be treated in Section 5).}

\textbf{Our response:}

\niemnote{This will be addressed somewhat by the changes discussed above; but Dan, could you help with this?}
We view the principles presented at the beginning as the main outcomes\slash results of this work, with the process of producing them (discussed in the new Section 3) based on a synthesis of information from the use cases and related work. Then, Section 6 (previously 5) discusses the ``results''.
Our modifications to the structure of the paper, and changes we hope improve the logical flow, should help indicate these connections better.

### 2016-07-21 sc-principles/rebuttal/rebuttal.tex

\textbf{Our response:}
\asnote{Perhaps we should be adding a short paragraph outlining how we believe that ultimately academic publishing should be moving towards sharing all of the products of researcher activity. This work is primarily about making software a citable entity which is just one part of a much larger change in the scholarly ecosystem.}

\niemnote{Dan, can you do this?} \katznote{I was hoping Arfon might do this one}

\item \textbf{Reviewer comment:}
\emph{This paper doesn't have an experimental design in the strict sense, as it is more of a position paper than a research article. The PeerJ guidelines state that ``the submission should clearly define the research question'', which is currently not the case for this paper. However, I see a research question between the lines, which could be phrased as ``how can citations be applied to software products to account for their increasing importance in scientific research?''. By making such a research question explicit, the PeerJ requirements can be met.}

\textbf{Our response:}
We agree that this paper is more of a position paper than research article, and thus that creating a research question would be an artificial construct. We are willing to make this change if required, but feel it wouldn't add much to the paper.

We modeled our process on the work done by the FORCE2016 Data Citation group, which included publishing a \emph{PeerJ CS} paper (\url{https://peerj.com/articles/cs-1/}) which was written in a similar manner to our paper.

### 2016-07-21 sc-principles/rebuttal/rebuttal.tex

\textbf{Our response:}
We agree that this paper is more of a position paper than research article, and thus that creating a research question would be an artificial construct. We are willing to make this change if required, but feel it wouldn't add much to the paper.

We modeled our process on the work done by the FORCE2016 Data Citation group, which included publishing a \emph{PeerJ CS} paper (\url{https://peerj.com/articles/cs-1/}) which was written in a similar manner to our paper.

\item \textbf{Reviewer comment:}
\emph{The use cases described in Section 3 form the main method to answer the implicit research question. Given the importance of these use cases for this paper, I think reference [18] with the details about these use cases should be published in a more official way, either on a site like ArXiv or FigShare, or maybe even as supplemental material or appendix for this paper. I think having these use cases in the appendix of this paper would be the best solution, which would also increase the impact of these use cases and would strengthen the paper in general.}

\textbf{Our response:}
We agree, and have added the full use cases text (with some edits for clarity and completion) as the new Appendix B for completeness.
We also added the comments (with our responses) made publicly following the presentation of the draft principles document at the FORCE2016 confernece, as Appendix C.

### 2016-07-21 sc-principles/software-citation-principles.tex
added indexed citations as + to use case 5

5.\ Get credit for software development          & \textbullet & \textbullet & \textbullet & + &             & \textbullet & \textbullet &             &             &             &             & Researcher, software engineer \\

>>>>

5.\ Get credit for software development          & \textbullet & \textbullet & \textbullet & + &             & \textbullet & \textbullet & + &             &             &             & Researcher, software engineer \\
